\begin{abstract}
Truly connected experiences are the key quality of room-scale virtual reality (VR). Here, the freedom to move promises natural sensory experiences stimulating a feeling of presence. However, users differ in their eagerness to move, some prefer movement by teleportation while others would keep walking forever. Such individual differences challenge the inclusive design necessary for bestseller applications. Further, user research frequently relies on aggregated data, missing the spatial context beneficial to insightful reports. 

We propose to study user behavior with `room-scale' VR resolution using parametric maps based on GLM, general linear modeling. In our study, participants explored \textit{invisible} mazes touching hidden walls for brief moments of visual guidance. We demonstrate the approach by showing that experienced presence correlated with where participants spent their time exploring the VR. We found an increase in presence coinciding with more time spent in the center of the maze paths and in segments critical for navigational success. Our proposed method elucidated spatial dependence of user experience in VR thereby proving its usefulness to conduct user research in room-scale VR applications.
\end{abstract}
% 150 words!
% in the end use hemingway app (http://www.hemingwayapp.com) to increase readability
% Word count is 190 and must be 150

%old
%The use of head-mounted virtual reality (VR) to induce presence in a computer simulated world has proven to significantly increase the ecological validity of this medium. In VR, illusions of various kinds (place illusion, plausibility illusion, etc.) occur at the same time for the user to feel present. Most prominently, the embodiment illusion has proven to elicit 'realistic' behavioral as well as physiological responses, when a strong emotional stimulus such as virtual hurting of an embodied rubber hand is provided. Yet, to be able to employ VR and claim ecological validity for less emotional stimuli, the level of presence must be accounted for.
%Designing remote interactions that induce truly connected social experiences is one of the great promises of room-scale VR. 
%We show that the level of presence impacts free spatial exploration behavior in a large scale VR navigation paradigm. Here, we investigate the impact of ongoing motor behavior with an established presence metric demonstrating an analysis framework with high resolution of user behavior in VR space. We observed participants with higher presence to exhibit higher spatial awareness by spending more time at navigationally relevant segments. Ultimately, the analysis approach links presence to individual differences in video game experience, sex, and spatial perspective taking abilities, confirming that user characteristics are a defining part of the presence construct.
%Video game experience, biological sex as well as spatial perspective taking skills proved to be significant predictors of a rich presence experience and were able to predict presence to within 3/4 of a point accuracy on a standard questionnaire scale. 
